---
date: "`r Sys.Date()`"
#author: "Your Name"
title: "Planning Template"
output: 
  officedown::rdocx_document:
    mapstyles:
      Normal: ['First Paragraph']
params:
  muni: NA
  data: NA
  moe_reports: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.cap = TRUE)
library(officedown)
library(officer)
library(dplyr)
library(stringr)

# fp <- fp_par(
#   text.align = "center", 
#   padding.bottom = 20, padding.top = 120, 
#   border.bottom = fp_border(style = "none"),
#   border.left = fp_border(style = "none"))
# 
# ft <- fp_text(shading.color='#EFEFEF', bold = TRUE)

fp_text_data <- fp_text(font.size = 9)
fp_text_label <- fp_text(font.size = 10)
fp_text_title <- fp_text(font.size = 12)


chart_default_theme <- mschart_theme(
  main_title = fp_text(font.size = 12), 
  axis_title_x = fp_text(font.size = 10), 
  axis_title_y = fp_text(font.size = 10),
  legend_text = fp_text(font.size = 9),
  grid_major_line_x = fp_border(color = "#D9D9D9", style = "solid", "width" = .75),
  grid_major_line_y = fp_border(color = "#D9D9D9", style = "solid", "width" = .75)
)

```

```{r insert_chart, include=FALSE}
#utility function to insert a mschart editable chart into the doc
insert_chart = function(chart_to_insert, id) {
#Create a doc object using officer. Add chart.
  doc <-
    officer::read_docx() %>%
    body_add_chart(chart = chart_to_insert, style = "graphic title", height = 5, width = 7)

  #Save document to a folder
  print(doc, target = paste0("placeholder_", id, ".docx"))

  #Pour that document into the rmarkdown
  block_pour_docx(paste0("placeholder_", id, ".docx"))
}
```


```{r variables,  include=FALSE}

pop_trend_vars <- c("population_1980",
                    "population_1990",
                    "population_2000",
                    "population_2010",
                    "population_1970",
                    "Population")

race_vars_nh <- c("nh_White alone", 
               "nh_Black or African American alone", 
               "nh_American Indian and Alaska Native alone", 
               "Hispanic or Latino (any race)",
               "nh_Asian alone",
               "nh_Native Hawaiian and other Pacific Islander alone",
               "nh_Some other race alone",
               "nh_Two or more races")

race_vars <- c("White alone", 
               "Black or African American alone", 
               "American Indian and Alaska Native alone", 
               "Hispanic or Latino (any race)",
               "Asian alone",
               "Native Hawaiian and other Pacific Islander alone",
               "Some other race alone",
               "Two or more races")

age_gender_vars <- c(
  "Median age",
  "Percent under 18",
  "Percent 65 and over",
  "Percent female",
  "Percent male"
)

age_gender_2010_vars <- c(
  "2010_Median age",
  "2010_Percent under 18",
  "2010_Percent 65 and over",
  "2010_Percent female",
  "2010_Percent male"
)

education_vars <- c(
  "Less than 9th grade", 
  "9th to 12th grade, no diploma", 
  "High school graduate (or equivalent)", 
  "Some college, no degree", 
  "Associate's degree", 
  "Bachelor's degree", 
  "Graduate or professional degree"
)

cost_burden_vars <- c(
  "Renters",
  "Mortgage holders",
  "Owned home"
)

poverty_vars <- c(
  "Poverty under 18 years",
  "Poverty 18 to 64 years",
  "Poverty 65 years and over"
)

housing_unit_vars <- c(
  "Housing units",
  "2010_Housing units",
  "2000_Housing units"
)

structure_type_vars <- c(
  "1 unit, detached",
  "1 unit, attached",
  "Multiple family",
  "Mobile home/other"
)

vacancy_vars <- c(
  "Homeowner vacancy",
  "Rental vacancy"
)

#for the progress bar
num_sections <- 36
cur_section <- 1

iterate_progress_bar <- function() {
  shiny::setProgress(cur_section/num_sections)
  cur_section <<- cur_section + 1
}

#for data source info
acs_cur_year <- "2022"
```


\newpage


# Demographic Trends

<br>
<br>

## Population Trends

<br>
<br>

### Summary Table
<br>
<br>

```{r population_trend_table, echo=FALSE}
#TODO - when I start including neighboring communities, will need to update this

#select the correct data
pop_data <- params$data %>%
  filter(Variable %in% pop_trend_vars) %>% 
  mutate(Variable = case_when(Variable == "Population" ~ "population_2020",
                              TRUE ~ Variable)) %>% 
  #transform to match the CARPC table
  mutate(Variable = substr(Variable, 12, 100)) %>% 
  pivot_longer(2:4) %>% 
  pivot_wider(names_from = Variable) %>% 
  select(name, `1980`, `1990`, `2000`, `2010`, `2020`) %>% 
  mutate(`Population Change 2010-2020` = `2020` - `2010`) %>% 
  #format with comma thousand separator
  mutate(across(2:7, ~ str_trim(format(.x, big.mark = ",", scientific = FALSE))))

#display the table
#head(pop_data, n=3)
flextable(pop_data) %>%
  set_caption("Population by Decade") %>% 
  autofit(add_w = 0)

iterate_progress_bar()
```
Source: 2020, 2010, 2000, 1990, 1980 Decennial census data

\newpage

### Summary Chart

<br>
<br>

```{r population_trend_graph, echo=FALSE}

#select the correct data
pop_data <- params$data %>%
#pop_data <- all_data %>%
  filter(Variable %in% pop_trend_vars) %>% 
  mutate(Variable = case_when(Variable == "Population" ~ "population_2020",
                              TRUE ~ Variable)) %>% 
  mutate(Variable = substr(Variable, 12, 100)) %>%
  select(1:2) %>% 
  #order correctly
  pivot_longer(2) %>% 
  arrange(Variable) %>% 
  mutate(Variable = factor(Variable, levels=unique(as.character(Variable))))

#display the chart
pop_chart <-
  ms_barchart(
  data = pop_data,
  x = "Variable",
  y = "value"
  ) %>%
  chart_labels(title = paste0(params$muni, " Population 1970-2020"), xlab = "Year", ylab = "Population") %>% 
  set_theme(chart_default_theme) %>% 
  chart_theme(legend_position = "n") %>% 
  chart_ax_y(num_fmt = "#,##0") %>% 
  chart_data_labels(num_fmt = "#,###", position = "outEnd", show_val = T) %>% 
  chart_labels_text(fp_text_data)

insert_chart(pop_chart, "population")

iterate_progress_bar()
```
Source: 2020, 2010, 2000, 1990, 1980, 1970 Decennial census data

\newpage


## Age & Gender

<br>
<br>

### Summary Tables

<br>
<br>

```{r age_gender_table, echo = FALSE}

age_data_s1 <- params$data %>%
  filter(Variable %in% age_gender_vars) %>% 
   rename_with(~paste0("2020_", .), 2:4)

age_data_s2 <- params$data %>%
  filter(Variable %in% age_gender_2010_vars) %>% 
   rename_with(~paste0("2010_", .), 2:4) %>% 
  mutate(Variable = substr(Variable, 6, 100))

age_data <- full_join(age_data_s1, age_data_s2, join_by(Variable == Variable)) %>% 
  #order correctly
  select(Variable, !!as.name(paste0("2010_", params$muni)), !!as.name(paste0("2020_", params$muni)), `2010_Dane County`, `2020_Dane County`, `2010_State of Wisconsin`, `2020_State of Wisconsin` )

#using flextable to merge cells and fit CARPC table design
age_table <- flextable(age_data) %>%
  set_header_labels(values = c("", "2010", "2020", "2010", "2020", "2010", "2020")) %>% 
  add_header_row(
  colwidths = c(1, 2, 2, 2),
  values = c("", params$muni, "Dane County", "State of Wisconsin")
  ) %>%
  set_caption("Age Summary") %>% 
  align(align = "center", part = "all") %>% 
  autofit(add_w = 0)

age_table

iterate_progress_bar()
```
Source: 2020, 2010 Decennial census data

\newpage

```{r age_gender_table_brackets, echo = FALSE}

age_graph_data_percent_table_s1 <- params$data %>%
  #shortcut to find the right variables
  filter(grepl("^percent_", Variable)) %>% 
  #reformat data
  mutate(Variable = substr(Variable, 9, 50)) %>% 
  mutate(group = word(Variable, 1)) %>% 
  mutate(Variable = word(Variable, 3, -1)) %>% 
  mutate(Variable = factor(Variable, levels=unique(as.character(Variable)))) %>% 
  group_by(Variable) %>% 
  #sum into brackets, dropping gender division
  summarise(`2020_community` = sum(!!as.name(params$muni)), `2020_Dane County` = sum(`Dane County`), `2020_State of Wisconsin` = sum(`State of Wisconsin`)) 

age_graph_data_percent_table_s2 <- params$data %>%
  #shortcut to find the right variables
  filter(grepl("^2010_percent_", Variable)) %>% 
  #reformat data
  mutate(Variable = substr(Variable, 9, 50)) %>% 
  mutate(group = word(Variable, 1)) %>% 
  mutate(Variable = word(Variable, 3, -1)) %>%
  mutate(Variable = factor(Variable, levels=unique(as.character(Variable)))) %>% 
  group_by(Variable) %>% 
  #sum into brackets, dropping gender division
  summarise(`2010_community` = sum(!!as.name(params$muni)), `2010_Dane County` = sum(`Dane County`), `2010_State of Wisconsin` = sum(`State of Wisconsin`))

age_graph_data_percent_table <- left_join(age_graph_data_percent_table_s1, age_graph_data_percent_table_s2, join_by(Variable == Variable)) %>% 
  #order correctly
  select(Variable, `2010_community`, `2020_community`, `2010_Dane County`, `2020_Dane County`, `2010_State of Wisconsin`, `2020_State of Wisconsin` )

#using flextable to merge cells and fit CARPC table design
age_bracket_table <- flextable(age_graph_data_percent_table) %>%
  set_header_labels(values = c("", "2010", "2020", "2010", "2020", "2010", "2020")) %>% 
  add_header_row(
  colwidths = c(1, 2, 2, 2),
  values = c("", params$muni, "Dane County", "State of Wisconsin")
  ) %>%
  set_caption("Age Bracket by Percent") %>% 
  align(align = "center", part = "all") %>% 
  autofit(add_w = 0)

age_bracket_table

iterate_progress_bar()
```
Source: 2020, 2010 Decennial census data

\newpage


### Municipality

<br>
<br>

```{r age_data, include=FALSE}
age_graph_data_percent <- params$data %>%
  #shortcut to find the right variables
  filter(grepl("^percent_", Variable)) %>% 
  #reformat data for graphing
  mutate(Variable = substr(Variable, 9, 50)) %>% 
  mutate(group = word(Variable, 1)) %>% 
  mutate(Variable = word(Variable, 3, -1))

age_graph_data_count <- params$data %>%
  filter(grepl("^value_", Variable)) %>%
  #reformat data for graphing
  mutate(Variable = word(Variable, 3, -1)) %>%
  #order correctly
  mutate(Variable = factor(Variable, levels=unique(as.character(Variable)))) %>% 
  group_by(Variable) %>%
  summarise(total = sum(!!as.name(params$muni)))
```


```{r age_p_muni, echo=FALSE}
age_p_muni <-
  ms_barchart(
  data = age_graph_data_percent %>%
    select(Variable, !!as.name(params$muni), group) %>% 
    #order correctly
    mutate(Variable = factor(Variable, levels=unique(as.character(Variable)))),
  x = "Variable",
  y = params$muni, group = "group"
  ) %>% 
  chart_settings(dir = "horizontal", overlap = -50) %>% 
  chart_labels(title = paste0("Female & Male Population by Age Group (", params$muni, ")"), xlab = "Age Group", ylab = "Percent of Population") %>% 
  set_theme(chart_default_theme) %>% 
  chart_theme(title_x_rot = 270, title_y_rot = 0) %>% 
  chart_ax_y(num_fmt = "#,###.0\\%")


insert_chart(age_p_muni, "age_p_muni")

iterate_progress_bar()
```
Source: 2020 Decennial census data

\newpage


```{r age_p_muni_dual, echo=FALSE}

age_graph_data_percent_dual <- age_graph_data_percent %>%
  select(Variable, !!as.name(params$muni), group) %>% 
  #make male category values negative to format graph correctly
  mutate((!!as.name(params$muni)) := case_when(group == "Male" ~ !!as.name(params$muni) * -1,
                                   TRUE ~ !!as.name(params$muni)))

age_p_muni_dual <-
  ms_barchart(
  data = age_graph_data_percent_dual %>%
    #order correctly
    mutate(Variable = factor(Variable, levels=unique(as.character(Variable)))),
  x = "Variable",
  y = params$muni, group = "group"
  ) %>% 
  chart_settings(dir = "horizontal", overlap = 100) %>% 
   chart_labels(title = paste0("Female & Male Population by Age Group (", params$muni, ")"), xlab = "Age Group", ylab = "Percent of Population") %>% 
  set_theme(chart_default_theme) %>% 
  chart_theme(title_x_rot = 270, title_y_rot = 0) %>% 
  chart_ax_x(tick_label_pos = "low") %>% 
  chart_ax_y(num_fmt = "#,##0\\%;[Black]#,##0\\%")

insert_chart(age_p_muni_dual, "age_p_muni_dual")

iterate_progress_bar()
```
Source: 2020 Decennial census data

\newpage

```{r age_c_muni, echo=FALSE}

age_c_muni <-
  ms_barchart(
  data = age_graph_data_count,
  x = "Variable",
  y = "total"
  ) %>% 
  chart_settings(dir = "horizontal", overlap = -50) %>% 
  chart_labels(title = paste0("Population by Age Group (", params$muni, ")"), xlab = "Age Group", ylab = "Count of Population") %>% 
  set_theme(chart_default_theme) %>% 
  chart_theme(title_x_rot = 270, title_y_rot = 0, legend_position = "n") %>% 
  chart_ax_y(num_fmt = "#,##0")


insert_chart(age_c_muni, "age_c_muni")

iterate_progress_bar()
```
Source: 2020 Decennial census data

\newpage


### County

<br>
<br>

```{r age_p_county, echo=FALSE}

age_p_county <-
  ms_barchart(
  data = age_graph_data_percent %>%
    select(Variable, `Dane County`, group) %>% 
    #order correctly
    mutate(Variable = factor(Variable, levels=unique(as.character(Variable)))),
  x = "Variable",
  y = "Dane County", group = "group"
  ) %>% 
  chart_settings(dir = "horizontal", overlap = -50) %>% 
  chart_labels(title = "Female & Male Percent Population by Age Group (Dane County)", xlab = "Age Group", ylab = "Percent of Population") %>% 
  set_theme(chart_default_theme) %>% 
  chart_theme(title_x_rot = 270, title_y_rot = 0) %>% 
  chart_ax_y(num_fmt = "#,###.0\\%")


insert_chart(age_p_county, "age_p_county")

iterate_progress_bar()
```
Source: 2020 Decennial census data

\newpage

```{r age_p_county_dual, echo=FALSE}
age_graph_data_percent_dual <- age_graph_data_percent %>%
  select(Variable, `Dane County`, group) %>%
  #make male category values negative to format graph correctly
  mutate(`Dane County` = case_when(group == "Male" ~ `Dane County` * -1,
                                   TRUE ~ `Dane County`))

age_p_county_dual <-
  ms_barchart(
  data = age_graph_data_percent_dual %>%
    #order correctly
    mutate(Variable = factor(Variable, levels=unique(as.character(Variable)))),
  x = "Variable",
  y = "Dane County", group = "group"
  ) %>% 
  chart_settings(dir = "horizontal", overlap = 100) %>% 
  chart_labels(title = "Female & Male Percent Population by Age Group (Dane County)", xlab = "Age Group", ylab = "Percent of Population") %>% 
  set_theme(chart_default_theme) %>% 
  chart_theme(title_x_rot = 270, title_y_rot = 0) %>% 
  chart_ax_x(tick_label_pos = "low") %>% 
  chart_ax_y(num_fmt = "#,##0\\%;[Black]#,##0\\%")

insert_chart(age_p_county_dual, "age_p_county_dual")

iterate_progress_bar()
```
Source: 2020 Decennial census data

\newpage

### State

<br>
<br>

```{r age_p_state, echo=FALSE}

age_p_state <-
  ms_barchart(
  data = age_graph_data_percent %>%
    select(Variable, `State of Wisconsin`, group) %>% 
    #order correctly
    mutate(Variable = factor(Variable, levels=unique(as.character(Variable)))),
  x = "Variable",
  y = "State of Wisconsin", group = "group"
  ) %>% 
  chart_settings(dir = "horizontal", overlap = -50) %>% 
  chart_labels(title = "Female & Male Percent Population by Age Group (WI)", xlab = "Age Group", ylab = "Percent of Population") %>% 
  set_theme(chart_default_theme) %>% 
  chart_theme(title_x_rot = 270, title_y_rot = 0) %>% 
  chart_ax_y(num_fmt = "#,###.0\\%")


insert_chart(age_p_state, "age_p_state")

iterate_progress_bar()
```
Source: 2020 Decennial census data

\newpage

```{r age_p_state_dual, echo=FALSE}

age_graph_data_percent_dual <- age_graph_data_percent %>%
  select(Variable, `State of Wisconsin`, group) %>% 
  #make male category values negative to format graph correctly
  mutate(`State of Wisconsin` = case_when(group == "Male" ~ `State of Wisconsin` * -1,
                                   TRUE ~ `State of Wisconsin`))

age_p_state_dual <-
  ms_barchart(
  data = age_graph_data_percent_dual %>%
    #order correctly
    mutate(Variable = factor(Variable, levels=unique(as.character(Variable)))),
  x = "Variable",
  y = "State of Wisconsin", group = "group"
  ) %>% 
  chart_settings(dir = "horizontal", overlap = 100) %>% 
  chart_labels(title = "Female & Male Percent Population by Age Group (WI)", xlab = "Age Group", ylab = "Percent of Population") %>% 
  set_theme(chart_default_theme) %>% 
  chart_theme(title_x_rot = 270, title_y_rot = 0) %>% 
  chart_ax_x(tick_label_pos = "low") %>% 
  chart_ax_y(num_fmt = "#,##0\\%;[Black]#,##0\\%")

insert_chart(age_p_state_dual, "age_p_state_dual")

iterate_progress_bar()
```
Source: 2020 Decennial census data


\newpage

## Race & Ethnicity

<br>
<br>

```{r race_data, include=FALSE}
#select the correct data

race_data_nh <- params$data %>%
  filter(Variable %in% race_vars_nh) %>% 
    #get rid of the prefixes for the sake of table/chart labels
  mutate(Variable = case_when(Variable != "Hispanic or Latino (any race)" ~ substr(Variable, 4, 200),
                              TRUE ~ Variable))
race_data <- params$data %>%
  filter(Variable %in% race_vars) %>% 
  #reorder to display correctly in table
  arrange(factor(Variable, levels=unique(as.character(race_data_nh$Variable))))
```

### Summary Tables

<br>
<br>

In this table, Hispanic or Latino is included as a separate category, regardless of any other race or ethnicity selected.

```{r race_table_nh, echo=FALSE}
#display the table
#head(race_data_nh, n=length(race_vars_nh))
flextable(race_data_nh) %>% 
  set_caption("Population by Race and Ethnicity (%)") %>% 
  autofit(add_w = 0)

iterate_progress_bar()
```
Source: 2020 Decennial census data

\newpage

```{r race_table, echo=FALSE}
#display the table
#head(race_data, n=length(race_vars))
flextable(race_data) %>% 
  set_caption("Population by Race and Ethnicity (%)") %>%
  autofit(add_w = 0)

iterate_progress_bar()
```
Source: 2020 Decennial census data

\newpage

### Summary Charts

<br>
<br>

In this chart, Hispanic or Latino is included as a separate category, regardless of any other race or ethnicity selected.

```{r race_graph_nh, echo=FALSE, fig.id = "tsplot"}
#display the chart
race_chart_nh <-
  ms_barchart(
  data = race_data_nh %>% 
    pivot_longer(2:4) %>% 
    mutate(name = factor(name, levels=c("State of Wisconsin", "Dane County", params$muni))), 
  x = "name",
  y = "value", group = "Variable"
  ) %>% 
  as_bar_stack(dir = "horizontal") %>% 
  chart_labels(title = "Population by Race and Ethnicity", xlab = "", ylab = "Percent of Population") %>% 
  chart_ax_y(num_fmt = "#,##0\\%", limit_max = 100) %>%
  set_theme(chart_default_theme) %>% 
  chart_theme(title_y_rot = 0) %>% 
  #make the colors color blind friendly
  chart_data_fill(c("American Indian and Alaska Native alone" = "#88ccee", 
                    "Asian alone" = "#44aa99",
                    "Black or African American alone" = "#117733", 
                    "Hispanic or Latino (any race)" = "#332288",
                    "Native Hawaiian and other Pacific Islander alone" = "#ddcc77",
                    "Some other race alone" = "#999933",
                    "Two or more races" = "#cc6677",
                    "White alone" = "#882255"
               )) %>% 
  #these data labels need custom formatting to be readable
  chart_data_labels(num_fmt = "0.0\\%", position = "ctr", show_val = T) %>% 
  chart_labels_text(fp_text_data)



insert_chart(race_chart_nh, "race_nh")

iterate_progress_bar()
```
Source: 2020 Decennial census data

\newpage

```{r race_graph, echo=FALSE, fig.id = "tsplot"}
#display the chart
race_chart <-
  ms_barchart(
  data = race_data %>% 
    #remove hispanic/latino category, doesn't add up to 100% otherwise
    filter(Variable != "Hispanic or Latino (any race)") %>% 
    pivot_longer(2:4) %>% 
    mutate(name = factor(name, levels=c("State of Wisconsin", "Dane County", params$muni))), 
  x = "name",
  y = "value", group = "Variable"
  ) %>% 
  as_bar_stack(dir = "horizontal") %>% 
  chart_labels(title = "Population by Race and Ethnicity", xlab = "", ylab = "Percent of Population") %>% 
  chart_ax_y(num_fmt = "#,##0\\%", limit_max = 100) %>% 
  set_theme(chart_default_theme) %>% 
  chart_theme(title_y_rot = 0) %>% 
  #make the colors more accessible
  chart_data_fill(c("American Indian and Alaska Native alone" = "#88ccee", 
                    "Asian alone" = "#44aa99",
                    "Black or African American alone" = "#117733", 
                    "Native Hawaiian and other Pacific Islander alone" = "#332288",
                    "Some other race alone" = "#ddcc77",
                    "Two or more races" = "#999933",
                    "White alone" = "#cc6677"
               )) %>% 
  chart_data_labels(num_fmt = "0.0\\%", position = "ctr", show_val = T) %>% 
  chart_labels_text(fp_text_data)



insert_chart(race_chart, "race")

iterate_progress_bar()
```
Source: 2020 Decennial census data

\newpage


## Education

<br>
<br>

### Summary Table

<br>
<br>


```{r education_data, include=FALSE}
#select the correct data
education_data <- params$data %>%
  filter(Variable %in% education_vars)
  
```

```{r education_table, echo=FALSE}
#display the table
#head(education_data, n=length(education_vars))
flextable(education_data) %>% 
  set_caption("Educational Attainment for Population 25+ (%)") %>% 
  autofit(add_w = 0)

iterate_progress_bar()
```
Source: `r acs_cur_year` 5-year ACS data 

\newpage

### Summary Chart

<br>
<br>

```{r education_graph, echo=FALSE, fig.id = "tsplot"}
#display the chart
education_chart <-
  ms_barchart(
  data = education_data %>% 
    pivot_longer(2:4) %>% 
    mutate(name = factor(name, levels=c("State of Wisconsin", "Dane County", params$muni))) %>% 
    mutate(Variable = factor(Variable, levels = education_vars)), 
  x = "name",
  y = "value", group = "Variable"
  ) %>% 
  as_bar_stack(dir = "horizontal") %>% 
  chart_labels(title = "Educational Attainment for Population 25+", xlab = "", ylab = "Percent of Population") %>% 
  chart_ax_y(num_fmt = "#,##0\\%",  limit_max = 100) %>% 
  set_theme(chart_default_theme) %>% 
  chart_theme(title_y_rot = 0) %>% 
  chart_data_fill(c("Less than 9th grade" = "#88ccee", 
  "9th to 12th grade, no diploma" = "#44aa99", 
  "High school graduate (or equivalent)" = "#117733", 
  "Some college, no degree" = "#332288", 
  "Associate's degree" = "#ddcc77", 
  "Bachelor's degree" = "#999933", 
  "Graduate or professional degree" = "#cc6677"
  )) %>% 
  chart_data_labels(num_fmt = "0.0\\%", position = "ctr", show_val = T) %>% 
  chart_labels_text(fp_text_data)

insert_chart(education_chart, "edu")

iterate_progress_bar()
```
Source: `r acs_cur_year` 5-year ACS data

\newpage

## Income

<br>
<br>

### Summary Chart

<br>
<br>

```{r median_income, echo=FALSE}
#graph for median income
median_income_data <- params$data %>%
  filter(Variable %in% c("Median household income in the past 12 months (in 2022 inflation-adjusted dollars)", "Median family income in the past 12 months (in 2022 inflation-adjusted dollars)")) %>%
  mutate(Variable = case_when(Variable == "Median household income in the past 12 months (in 2022 inflation-adjusted dollars)" ~ "Median Household Income",
         Variable == "Median family income in the past 12 months (in 2022 inflation-adjusted dollars)" ~ "Median Family Income")) %>%
  pivot_longer(2:4)

#display the chart
median_income_chart <-
  ms_barchart(
  data = median_income_data %>% 
    mutate(name = factor(name, levels=c(params$muni, "Dane County", "State of Wisconsin"))),
  x = "Variable",
  y = "value", group = "name"
  ) %>%
  chart_labels(title = "Median Income in the past 12 months (in 2022 inflation-adjusted dollars)", xlab = "", ylab = "Income") %>% 
  chart_settings(overlap = -5) %>% 
  chart_ax_y(num_fmt = "$#,##0") %>% 
  chart_data_labels(num_fmt = "$#,###", position = "outEnd", show_val = T) %>% 
  chart_labels_text(fp_text_data) %>% 
  set_theme(chart_default_theme)

insert_chart(median_income_chart, "med_income")

iterate_progress_bar()
```
Source: `r acs_cur_year` 5-year ACS data

\newpage

### Municipality Income Distribution

<br>
<br>

```{r income_brackets, echo=FALSE}
#graph for income distribution
income_dist_data <- params$data %>%
  slice(101:116) %>%
  pivot_longer(2:4) %>% 
   #order correctly
  mutate(Variable = factor(Variable, levels=unique(as.character(Variable)))) %>% 
  filter(name == params$muni)

#display the chart
income_dist_chart <-
  ms_barchart(
  data = income_dist_data,
  x = "Variable",
  y = "value"
  ) %>%
  chart_labels(title = "Household Income in the Past 12 Months (in 2022 Inflation-Adjusted Dollars)", xlab = "Income", ylab = "Percent of Population") %>% 
  chart_settings(dir = "horizontal") %>%
  set_theme(chart_default_theme) %>% 
  chart_theme(title_x_rot = 270, title_y_rot = 0, legend_position = "n") %>% 
  chart_ax_y(num_fmt = "#,##0\\%") %>% 
  chart_data_labels(num_fmt = "0.0\\%", position = "outEnd", show_val = T) %>% 
  chart_labels_text(fp_text_data)

insert_chart(income_dist_chart, "income_dist")

iterate_progress_bar()
```
Source: `r acs_cur_year` 5-year ACS data

\newpage

## Poverty

<br>
<br>

```{r poverty, echo=FALSE}
#graph for poverty
poverty_data <- params$data %>% 
  filter(Variable %in% poverty_vars) %>% 
  pivot_longer(2:4)

#display the chart
poverty_chart <-
  ms_barchart(
  data = poverty_data %>% 
    mutate(name = factor(name, levels=c(params$muni, "Dane County", "State of Wisconsin"))),
  x = "Variable",
  y = "value", group = "name"
  ) %>%
  chart_labels(title = "Poverty Rates by Age", xlab = "", ylab = "Percent of Population") %>% 
  chart_settings(overlap = -5) %>% 
  set_theme(chart_default_theme) %>% 
  chart_ax_y(num_fmt = "#,##0\\%") %>% 
  chart_data_labels(num_fmt = "0.0\\%", position = "outEnd", show_val = T) %>% 
  chart_labels_text(fp_text_data)

insert_chart(poverty_chart, "poverty")

iterate_progress_bar()
```
Source: `r acs_cur_year` 5-year ACS data


\newpage

# Labor Force & Employment

<br>
<br>

## Unemployment

<br>
<br>

```{r unemployment, echo=FALSE}
#graph for unemployment
unemployment_data <- params$data %>% 
  filter(Variable == "Percent unemployment") %>% 
  pivot_longer(2:4)

#display the chart
unemployment_chart <-
  ms_barchart(
  data = unemployment_data,
  x = "name",
  y = "value"
  ) %>%
  chart_labels(title = "Unemployment Rate (16 year olds and older)", xlab = "", ylab = "Percent of Population") %>%
  set_theme(chart_default_theme) %>% 
  chart_theme(legend_position = "n") %>% 
  chart_ax_y(num_fmt = "#,###.0\\%") %>% 
  chart_data_labels(num_fmt = "0.0\\%", position = "outEnd", show_val = T) %>% 
  chart_labels_text(fp_text_data)

insert_chart(unemployment_chart, "unemployment")

iterate_progress_bar()
```
Source: `r acs_cur_year` 5-year ACS data

\newpage

## Industry
<br>
<br>

```{r industry, echo=FALSE}
#graph for industry employment
industry_data <- params$data %>% 
  slice(120:132) %>% 
  pivot_longer(2:4)

#display the chart
industry_chart <-
  ms_barchart(
  data = industry_data %>% 
    mutate(name = factor(name, levels=c("State of Wisconsin", "Dane County", params$muni))),
  x = "Variable",
  y = "value", group = "name"
  ) %>%
  chart_labels(title = "Employment by Industry (16+ years old)", xlab = "Industry", ylab = "Percent of Population") %>% 
  chart_settings(dir = "horizontal", overlap = -50) %>% 
  set_theme(chart_default_theme) %>% 
  chart_theme(title_x_rot = 270, title_y_rot = 0) %>% 
  chart_ax_y(num_fmt = "#,##0\\%")

insert_chart(industry_chart, "industry")

iterate_progress_bar()
```
Source: `r acs_cur_year` 5-year ACS data

\newpage

## Labor Force

<br>
<br>

```{r labor_force, echo=FALSE}
#graph for labor force participation
labor_data <- params$data %>% 
  filter(Variable == "Labor force participation") %>% 
  pivot_longer(2:4)

#display the chart
labor_chart <-
  ms_barchart(
  data = labor_data,
  x = "name",
  y = "value"
  ) %>%
  chart_labels(title = "Labor Force Participation Rate (Population 16+ Years Old)", xlab = "", ylab = "Percent of Population") %>% 
  set_theme(chart_default_theme) %>% 
  chart_theme(legend_position = "n") %>% 
  chart_ax_y(limit_min = 0) %>% 
  chart_ax_y(num_fmt = "#,##0\\%") %>% 
  chart_data_labels(num_fmt = "0.0\\%", position = "outEnd", show_val = T) %>% 
  chart_labels_text(fp_text_data)

insert_chart(labor_chart, "labor")

iterate_progress_bar()
```
Source: `r acs_cur_year` 5-year ACS data

\newpage

# Housing

<br>
<br>

## Housing Stock Characteristics

<br>
<br>

```{r housing_unit_chart, echo = FALSE}
housing_unit_data <- params$data %>% 
  filter(Variable %in% housing_unit_vars) %>% 
  mutate(Variable = case_when(Variable == "Housing units" ~ "2020 Housing units",
                              Variable == "2010_Housing units" ~ "2010 Housing units",
                              Variable == "2000_Housing units" ~ "2000 Housing units")) 

flextable(housing_unit_data %>%
   #format with comma thousand separator
    mutate(across(2:4, ~ str_trim(format(.x, big.mark = ",", scientific = FALSE))))) %>% 
    set_caption("Number of Housing Units by Decade") %>% 
    autofit(add_w = 0)

iterate_progress_bar()
```
Source: 2020, 2010, 2000 Decennial census data

\newpage

```{r housing_unit_graph, echo = FALSE}

#display the chart
housing_unit_chart <-
  ms_barchart(
  data = housing_unit_data %>% 
    #only use the muni data
    pivot_longer(2:2) %>% 
    #rename and reorder the years
    mutate(Variable = substr(Variable, 1, 4)) %>% 
    arrange(Variable) %>% 
    mutate(Variable = factor(Variable, levels=unique(as.character(Variable)))),
  x = "Variable",
  y = "value"
  ) %>%
  chart_labels(title = "Number of Housing Units", xlab = "Year", ylab = "Total Housing Units") %>% 
  set_theme(chart_default_theme) %>% 
  chart_theme(legend_position = "n") %>% 
  chart_ax_y(num_fmt = "#,##0") %>% 
  chart_data_labels(num_fmt = "#,###", position = "outEnd", show_val = T) %>% 
  chart_labels_text(fp_text_data)


insert_chart(housing_unit_chart, "housing_unit")

iterate_progress_bar()
```
Source: 2020, 2010, 2000 Decennial census data

\newpage

```{r housing_age_table, echo = F}
#table for housing stock age

structure_age_data <- params$data %>% 
  slice(133:142)

flextable(structure_age_data %>%
   #only use muni data
     select(1:2) %>% 
   #format with comma thousand separator
      mutate(across(2:2, ~ str_trim(format(.x, big.mark = ",", scientific = FALSE))))) %>% 
   set_caption("Age of Housing Stock (%)") %>% 
  autofit(add_w = 0)

iterate_progress_bar()
```
Source: `r acs_cur_year` 5-year ACS data


\newpage


```{r housing_age_graph, echo=FALSE, fig.id = "tsplot"}
#graph for housing stock age

#display the chart
structure_age_chart <-
  ms_barchart(
  data = structure_age_data %>% pivot_longer(2:2),
  x = "Variable",
  y = "value"
  ) %>%
  chart_labels(title = "Age of Housing Stock", xlab = "Year Built", ylab = "Percent of Housing Stock") %>% 
  chart_settings(dir = "horizontal", overlap = -50) %>% 
  set_theme(chart_default_theme) %>% 
  chart_theme(title_x_rot = 270, title_y_rot = 0, legend_position = "n") %>% 
  chart_ax_y(num_fmt = "#,##0\\%") %>% 
  chart_data_labels(num_fmt = "0.0\\%", position = "outEnd", show_val = T) %>% 
  chart_labels_text(fp_text_data)


insert_chart(structure_age_chart, "structure_age")

iterate_progress_bar()
```
Source: `r acs_cur_year` 5-year ACS data

\newpage

```{r housing_unit_type_table, echo = F}
#table for housing stock age

structure_type_data <- params$data %>% 
 filter(Variable %in% structure_type_vars) 

flextable(structure_type_data) %>% 
   set_caption("Housing Unit Structure Type (%)") %>% 
  autofit(add_w = 0)

iterate_progress_bar()
```


\newpage

## Occupancy Characteristics

<br>
<br>

```{r homeownership, echo=FALSE}
#graph for homeownership
homeowner_data <- params$data %>% 
  filter(Variable == "Owner occupied") %>% 
  pivot_longer(2:4)

#display the chart
homeowner_chart <-
  ms_barchart(
  data = homeowner_data,
  x = "name",
  y = "value"
  ) %>%
  chart_labels(title = "Homeownership Rate", xlab = "", ylab = "Percent of Population") %>% 
  set_theme(chart_default_theme) %>% 
  chart_theme(legend_position = "n") %>% 
  chart_ax_y(limit_min = 0) %>% 
  chart_ax_y(num_fmt = "#,##0\\%") %>% 
  chart_data_labels(num_fmt = "0.0\\%", position = "outEnd", show_val = T) %>% 
  chart_labels_text(fp_text_data)


insert_chart(homeowner_chart, "homeowner")

iterate_progress_bar()
```
Source: `r acs_cur_year` 5-year ACS data

\newpage

```{r home_value, echo=FALSE}
#graph for median home value
home_value_data <- params$data %>%
  filter(Variable == "Median home value") %>% 
  pivot_longer(2:4)

#display the chart
home_value_chart <-
  ms_barchart(
  data = home_value_data,
  x = "name",
  y = "value"
  ) %>%
  chart_labels(title = "Median Home Value", xlab = "", ylab = "Value") %>% 
  set_theme(chart_default_theme) %>% 
  chart_theme(legend_position = "n") %>% 
  chart_ax_y(num_fmt = "$#,##0") %>% 
  chart_data_labels(num_fmt = "$#,###", position = "outEnd", show_val = T) %>% 
  chart_labels_text(fp_text_data)

insert_chart(home_value_chart, "home_value")

iterate_progress_bar()
```
Source: `r acs_cur_year` 5-year ACS data

\newpage

```{r housing_vacancy_table, echo = F}
#table for housing stock vacancy

vacancy_data <- all_data %>% 
 filter(Variable %in% vacancy_vars) 

flextable(vacancy_data) %>% 
   set_caption("Housing Vacancy (%)") %>% 
  autofit(add_w = 0)

iterate_progress_bar()
```
Source: `r acs_cur_year` 5-year ACS data

\newpage

## Housing Affordability

<br>
<br>

```{r cost_burden_table, echo=FALSE}
cost_burden_data <- params$data %>%
  filter(Variable %in% cost_burden_vars)

#display the table
#head(cost_burden_data, n=length(cost_burden_vars))
flextable(cost_burden_data) %>% 
  set_caption("Cost Burdened Households Paying 30%+ of Income for Housing (%)") %>% 
  autofit(add_w = 0)

iterate_progress_bar()
```
Source: `r acs_cur_year` 5-year ACS data

\newpage

```{r cost_burden_graph, echo=FALSE}
#graph for cost burden
cost_burden_data <- cost_burden_data %>%
  select(1:2) %>% 
  pivot_longer(2:2)

#display the chart
cost_burden_chart <-
  ms_barchart(
  data = cost_burden_data,
  x = "Variable",
  y = "value"
  ) %>%
  chart_labels(title = "Cost Burdened Households Paying 30%+ of Income for Housing", xlab = "", ylab = "Percent of Population") %>%
  set_theme(chart_default_theme) %>% 
  chart_theme(legend_position = "n") %>% 
  chart_ax_y(num_fmt = "#,##0\\%") %>% 
  chart_data_labels(num_fmt = "0.0\\%", position = "outEnd", show_val = T) %>% 
  chart_labels_text(fp_text_data)

insert_chart(cost_burden_chart, "cost_burden")

iterate_progress_bar()
```
Source: `r acs_cur_year` 5-year ACS data

\newpage


# Census Reporting

The American Community Survey (ACS) surveys a sample of the U.S. population, so includes a margin of error for each estimate. The estimate, margin of error (MOE), coefficient of variation (CV), and interpreted reliability are reported for each variable below. 

<br>

If a variable estimate was 0, the CV was set to 100% as suggested by Census Bureau guidelines. The reliability was calculated based on the CV: a CV of 12% or less was assigned high reliability; a CV above 12% but less than or equal to 40% was assigned medium reliability; a CV of more than 40% was assigned low reliability. This follows the ESRI methodology for quantifying reliability (https://www.esri.com/arcgis-blog/products/arcgis-living-atlas/mapping/margins-of-error-and-mapping/).

<br>

More information about the Census Bureau methodology can be found here: https://www.census.gov/content/dam/Census/library/publications/2018/acs/acs_general_handbook_2018_ch08.pdf. Note that the Decennial Census is a full population survey, so contains no reported margin of error.

<br>
<br>

## Municipality
<br>
<br>

```{r moe_muni, echo=FALSE}
head(params$moe_reports$muni, n=nrow(params$moe_reports$muni))
# flextable(params$moe_reports$muni) %>% 
#   autofit(add_w = 0)

iterate_progress_bar()
```


## County
<br>
<br>

```{r moe_county, echo=FALSE}
head(params$moe_reports$county, n=nrow(params$moe_reports$county))
# flextable(params$moe_reports$county) %>% 
#   autofit(add_w = 0)

iterate_progress_bar()
```


## State
<br>
<br>

```{r moe_state, echo=FALSE}
head(params$moe_reports$state, n=nrow(params$moe_reports$state))
# flextable(params$moe_reports$state) %>% 
#   autofit(add_w = 0)

iterate_progress_bar()
```
